---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r pkg-knitr-opts, include=FALSE}
hrbrpkghelpr::global_opts()
```

```{r badges, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::stinking_badges()
```

```{r description, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::yank_title_and_description()
```

## What's Inside The Tin

The following functions are implemented:

```{r ingredients, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::describe_ingredients()
```

## Installation

```{r install-ex, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::install_block()
```

## Usage

```{r lib-ex}
library(ggsolar)
library(ggplot2)

# current version
packageVersion("ggsolar")

```

## Sol

```{r sol, fig.width=6, fig.height=6, dev.args=list(bg="transparent")}
sol_orbits <- generate_orbits(sol_planets)

set.seed(1323) # this produced decent placements

placed_planets <- randomize_planet_positions(sol_orbits)

plot_orbits(
  orbits = sol_orbits, 
  planet_positions = placed_planets,
  label_planets = TRUE,
  label_family = hrbrthemes::font_es_bold
) +
  hrbrthemes::theme_ipsum_es(grid="") +
  coord_equal() +
  labs(
    title = "Sol",
    caption = "Pluto is 100% a planet"
  ) +
  theme_enhance_solar()
```

## Non-uniform Radii

We'll plot Sol's system with the square root of the actual radius AU's (which are `0.39`, `0.72`, `1.00`, `1.52`, `5.20`, `9.58`, `19.18`, `30.07`, `39.48`):

```{r sol-sqrt, fig.width=7, fig.height=7, dev.args=list(bg="transparent")}
sol_dist <- sqrt(c(0.39, 0.72, 1.00, 1.52, 5.20, 9.58, 19.18, 30.07, 39.48))
sol_orbits <- generate_orbits(sol_planets, radii = sol_dist, num_polygon_points = 1000)

set.seed(42)
sol_placements <- randomize_planet_positions(sol_orbits)

plot_orbits(
  orbits = sol_orbits, 
  planet_positions = sol_placements,
  label_planets = TRUE,
  label_family = hrbrthemes::font_es_bold
) +
  hrbrthemes::theme_ipsum_es(grid="") +
  coord_equal() +
  labs(
    title = "Sol System (Orbits AU Sqrt.)",
    subtitle = "Non-uniform Radii",
    caption = "Pluto is 100% a planet"
  ) +
  theme_enhance_solar()
```

## Custom Planet Placements!

We'll plot Sol's system with the square root of the actual radius AU's (which are `0.39`, `0.72`, `1.00`, `1.52`, `5.20`, `9.58`, `19.18`, `30.07`, `39.48`):

```{r sol-precise-sqrt, fig.width=7, fig.height=7, dev.args=list(bg="transparent")}
sol_dist <- sqrt(c(0.39, 0.72, 1.00, 1.52, 5.20, 9.58, 19.18, 30.07, 39.48))
sol_orbits <- generate_orbits(sol_planets, radii = sol_dist, num_polygon_points = 1000)

my_pos <- function(n) {
  seq(from = 0, to = 1, length.out = 9)
}

sol_placements <- randomize_planet_positions(sol_orbits, randomizer = my_pos)

plot_orbits(
  orbits = sol_orbits, 
  planet_positions = sol_placements,
  label_planets = TRUE,
  label_family = hrbrthemes::font_es_bold
) +
  hrbrthemes::theme_ipsum_es(grid="") +
  coord_equal() +
  labs(
    title = "Sol System (Orbits AU Sqrt.)",
    subtitle = "Custom placements",
    caption = "Pluto is 100% a planet"
  ) +
  theme_enhance_solar()
```


## Rando!

```{r rando, fig.width=6, fig.height=6, dev.args=list(bg="transparent")}
set.seed(42)
(rando_planets <- generate_random_planets(12))

rando_orbits <- generate_orbits(rando_planets)

set.seed(123) # this produced decent placements

placed_planets <- randomize_planet_positions(rando_orbits)

plot_orbits(
  orbits = rando_orbits, 
  planet_positions = placed_planets,
  label_planets = TRUE,
  label_family = hrbrthemes::font_es_bold
) +
  hrbrthemes::theme_ipsum_es(grid="") +
  coord_equal() +
  labs(
    title = "Rando System"
  ) +
  theme_enhance_solar()
```

## ggsolar Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a Contributor Code of Conduct. 
By participating in this project you agree to abide by its terms.
